Scalable and Modular Verified Compilation via Automated Proofs for Declarative Transformations.

### 2025-01-31 paper.tex
fix publication venue

My PhD clock started in Michealmas term 2023, meaning my submission
window is between October 2026 and September 2027, or between 21 and 33
months from now. Picking the lower end of that timeframe gives exactly 7
months per chapter, leaving the final year for writing up the thesis, which I'll
spend as follows.

\subsection*{High-Assurance Translation Validation for Compiler Optimizations
Targeted publication venue: PLDI}

>>>>

My PhD clock started in Michealmas term 2023, meaning my submission
window is between October 2026 and September 2027, or between 21 and 33
months from now. Picking the lower end of that timeframe gives exactly 7
months per chapter, leaving the final year for writing up the thesis.

Furthermore, I plan to translate each of the technical chapters described in this proposal into a paper, to be submitted at the designated venue.

\subsection*{High-Assurance Translation Validation for Compiler Optimizations}
Targeted publication venue: PLDI
